Modelling the travel time of transit vehicles in \rt through a GTFS-based road network using GPS vehicle locations

### 2019-08-10 anzjs2018/anzjs.tex
more ...

% Modelling transit vehicles to estimate the \rt traffic conditions in a public transport network}
\author{Tom Elliott\corrauth~and~Thomas~Lumley}
\affiliation{University of Auckland}
\address{
    Department of Statistics, University of Auckland, 
    Auckland 1142, New Zealand\\
    Email: \texttt{tom.elliott@auckland.ac.nz}
}
\ack{
    We would like to thank Auckland Transport for providing free,
    open access to the \rt data; and the Center for e-Research at the
    University of Auckland for providing and maintaining the virtual
    machine used in our work.
}

@@

\keywords{particle filter; transit modeling;
          transit networks; applications; gtfs}

>>>>

% Modelling transit vehicles to estimate the \rt traffic conditions in a public transport network}
\author{Tom Elliott\corrauth~and~Thomas~Lumley}
\affiliation{University of Auckland}
\address{
    Department of Statistics, University of Auckland, 
    Auckland 1142, New Zealand\\
    Email: \texttt{tom.elliott@auckland.ac.nz}
}
\ack{
    We would like to thank Auckland Transport for providing free,
    open access to the \rt data; and the Centre for e-Research at the
    University of Auckland for providing and maintaining the virtual
    machine used in our work.
}

@@

\keywords{particle filter; transit modelling;
          transit networks; applications; gtfs}
